\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Minimized margins
\usepackage{helvet} % Helvetica font, looks cleaner/modern
\renewcommand{\familydefault}{\sfdefault} % Set default font family to sans-serif
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor} % For custom colors
\usepackage{hyperref} % For links
\usepackage{fontawesome5} % For icons
\usepackage{titlesec} % For section formatting
\usepackage{enumitem} % For list formatting
\usepackage{tabularx} % For flexible tables
\usepackage{ragged2e} % For text alignment

%----------------------------------------------------------------------------------------
%	COLOR PALETTE (Premium Deep Blue & Gold/Grey)
%----------------------------------------------------------------------------------------
% Primary Theme Color: Deep Royal Navy
\definecolor{primary}{RGB}{10, 30, 60} 
% Accent Color: Muted Gold or Electric Blue (Using a sophisticated Slate Blue here)
\definecolor{accent}{RGB}{40, 90, 140}
% Text Colors
\definecolor{darktext}{RGB}{30, 30, 30}
\definecolor{lighttext}{RGB}{80, 80, 80}
\definecolor{linkcolor}{RGB}{0, 80, 160}

%----------------------------------------------------------------------------------------
%	CUSTOM COMMANDS & STYLING
%----------------------------------------------------------------------------------------

% Links
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    filecolor=linkcolor,      
    urlcolor=linkcolor,
}

% Header Name Style
\newcommand{\headername}[1]{
    {\Huge\bfseries\color{primary} #1}
}

% Section Headings
\titleformat{\section}
    {\Large\bfseries\color{primary}\uppercase} % Format
    {} % Label
    {0em} % Sep
    {} % Before-code
    [\titlerule] % After-code (Horizontal line)

% Subsection Headings (e.g. Job Titles)
\newcommand{\role}[2]{
    {\large\bfseries\color{darktext} #1} \hfill {\color{accent}\textbf{#2}}
}

% Company/Institution Name
\newcommand{\employer}[2]{
    {\color{lighttext}\textit{#1}} \hfill {\color{lighttext}\textit{#2}}
}

% Custom Bullet Points
\renewcommand\labelitemi{\color{accent}\small$\bullet$}

% Tighten lists
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=2pt}

%----------------------------------------------------------------------------------------
%	DOCUMENT CONTENT
%----------------------------------------------------------------------------------------
\begin{document}

%--- HEADER ---
\begin{center}
    \headername{Debdeep Sanyal} \\ \vspace{0.2em}
    {\color{accent}\large Android \& AI/ML Engineer} \\ \vspace{0.5em}
    
    \small
    \faPhone\ +91 7044692859 \quad
    \faMapMarker*\ Kolkata, India \quad
    \faEnvelope\ \href{mailto:sanyaldebdeep@gmail.com}{sanyaldebdeep@gmail.com} \\ \vspace{0.3em}
    \faLinkedin\ \href{https://www.linkedin.com/in/debdeep-sanyal-4a38901b2/}{LinkedIn Profile} \quad
    \faGithub\ \href{https://devdebsan.github.io/Portfolio/}{Portfolio}
\end{center}

\vspace{-1em}

%--- OBJECTIVE ---
\section*{Objective}
\vspace{-0.5em}
Android and AI/ML Engineer with \textbf{3 years of experience} building production Android systems and computer vision solutions. Experienced in real-time video analytics, model integration, and edge deployment, with a focus on scalable and reliable products.

%--- SKILLS ---
\section*{Technical Skills}
\vspace{-0.5em}
\begin{tabularx}{\textwidth}{@{}l X@{}}
    \textbf{\color{accent}Programming} & Kotlin, Java, Python, XML \\
    \textbf{\color{accent}Android Engineering} & Android SDK, Jetpack Compose, MVVM, RESTful APIs, SQLite, Firebase \\
    \textbf{\color{accent}Computer Vision} & OpenCV, ML Kit, TrackNet, InsightFace, DeepFace \\
    \textbf{\color{accent}Deep Learning} & CNN-based models, Object Detection/Tracking, Face Recognition \\
    \textbf{\color{accent}Models \& Architecture} & LSTM, BiLSTM, Transformer-based architectures \\
    \textbf{\color{accent}Training \& Optimization} & PyTorch, ONNX, TensorFlow Lite, CoreML, Quantization, Edge Deployment \\
    \textbf{\color{accent}Video Processing} & RTSP pipelines, GStreamer, FFmpeg, GPU-accelerated inference \\
    \textbf{\color{accent}Tools \& Systems} & Android Studio, Git, Google Cloud Console, Multithreading, Performance Tuning \\
\end{tabularx}

%--- EXPERIENCE ---
\section*{Professional Experience}
\vspace{-0.5em}

\role{Android \& AI/ML Engineer}{Feb 2022 – Present} \\
\employer{Vareli Tecnac Pvt. Ltd.}{Kolkata, India}
\begin{itemize}
    \item \textbf{Production Ownership:} Took ownership of multiple production mobile products, handling development, release, and post-deployment stability.
    \item \textbf{Scalable Architecture:} Designed scalable workflows focusing on performance, reliability, and user experience.
    \item \textbf{Real-Time Systems:} Integrated real-time data and media streams into applications, ensuring low latency in live environments.
    \item \textbf{ML Integration:} Collaborated with ML teams to integrate inference outputs into user-facing features, focusing on on-device processing and performance tuning.
    \item \textbf{Cross-Functional Leadership:} Coordinated with backend, QA, and hardware teams to deliver end-to-end production systems.
\end{itemize}

%--- PROJECTS ---
\section*{Key Projects}
\vspace{-0.5em}

\role{Play–Pause–Post (PPP): AI Sports Replay \& Analytics Platform}{Production}
\begin{itemize}
    \item \textbf{Real-Time Tracking:} Implemented live ball and shuttle tracking (TrackNet, 90\%+ accuracy) with continuous model tuning.
    \item \textbf{Computer Vision features:} Built court keypoint detection for localization and an automated line-calling system using bounce location geometry.
    \item \textbf{Optimization:} Optimized inference pipelines for \textbf{iOS/CoreML and GPU execution} to support low-latency replays.
    \item \textbf{Smart Watch Integration:} Extended line-calling and replay insights to an Android Watch app for real-time officiating.
    \item \textit{Tech:} TrackNet, Roboflow, CoreML, Android Watch, Geometric Mapping. \href{https://play.google.com/store/apps/details?id=com.vtpl.volley}{(Play Store Link)}
\end{itemize}
\vspace{0.3em}

\role{CCTV-Based Face Recognition \& Attendance Analytics}{Surveillance System}
\begin{itemize}
    \item \textbf{Custom ML Models:} Implemented custom face recognition trained on InsightFace/DeepFace backbones.
    \item \textbf{Pipeline Engineering:} Built reliable video ingestion using \textbf{GStreamer and RTSP}, automating attendance across multiple streams.
    \item \textbf{Analytics:} Generated heatmaps, headcounts, and time-based insights, improving robustness against occlusion and lighting changes.
\end{itemize}
\vspace{0.3em}

\role{V-Commute}{Enterprise Android Platform}
\begin{itemize}
    \item \textbf{Smart Tracking:} Implemented geofenced real-time commute tracking and dynamic Travel Allowance (TA) calculation.
    \item \textbf{Secure Auth:} Integrated biometric and face-based authentication (\textbf{99\%+ accuracy}) with anti-spoofing and offline support using a lightweight on-device model.
    \item \textbf{Financial Logic:} Designed automatic price management with hierarchy-wise approval workflows. \href{https://play.google.com/store/apps/details?id=com.vcommute.traveltracking}{(Play Store Link)}
\end{itemize}
\vspace{0.3em}

\role{V-Fleet}{Fleet Operations Platform}
\begin{itemize}
    \item \textbf{Offline-First:} Built an architecture supporting uninterrupted operations in low-network regions.
    \item \textbf{Real-Time Ops:} Enabled vehicle status tracking, trip synchronization, and operational insights. \href{https://play.google.com/store/apps/details?id=com.vareli.fleet}{(Play Store Link)}
\end{itemize}
\vspace{0.3em}

\role{V-Asset}{Asset Lifecycle Management}
\begin{itemize}
    \item \textbf{Security & Scanning:} Implemented JWT-based auth with RBAC and integrated QR/barcode scanning via ML Kit.
    \item \textbf{Compliance:} Implemented audit trails and asset history tracking. \href{https://play.google.com/store/apps/details?id=com.asset.assetmanagementproj}{(Play Store Link)}
\end{itemize}
\vspace{0.3em}

\role{iCan}{Accessibility App for Deaf Users}
\begin{itemize}
    \item \textbf{Inclusive Design:} Built sign-language video workflows and integrated speech-to-text/text-to-speech for two-way communication.
    \item \textbf{Education:} Designed assignment submission workflows to track learning progress.
    \item \textbf{Leadership:} Led a cross-functional team of 4 developers from design to delivery. \href{https://play.google.com/store/apps/details?id=com.vtpl.challenged}{(Play Store Link)}
\end{itemize}

%--- EDUCATION ---
\section*{Education}
\vspace{-0.5em}

\role{Master of Technology (M.Tech) in Computer Technology (AI \& DS)}{2024 – Present} \\
\employer{Jadavpur University}{Kolkata, India}

\vspace{0.3em}

\role{Bachelor of Technology (B.Tech) in CSE}{2019 – 2023} \\
\employer{I.K. Gujral Punjab Technical University}{Punjab, India}

\end{document}
